COG-ED Manuscript

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd
changed file navigation

  here::i_am("Manuscript.Rmd")

@@

  datalist_nback = lapply(list.files(here("Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  datalist_ED = lapply(list.files(here("Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

@@

  data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column

>>>>

  here::i_am("flag_project_root.txt")

@@

  datalist_nback = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  datalist_ED = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

@@

  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column
